% FPL 2026 Abstract Submission — 250 words max
% "Zero-DSP Ternary Transformer Inference on a $30 FPGA with Open-Source Toolchain"
% Deadline: March 20, 2026

\documentclass[conference]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{booktabs}

\begin{document}

\title{Zero-DSP Ternary Transformer Inference\\on a \$30 FPGA with Open-Source Toolchain}

\author{
\IEEEauthorblockN{Dmitrii Vasilev}
\IEEEauthorblockA{Trinity Project\\
\texttt{https://github.com/gHashTag/trinity}}
}

\maketitle

\begin{abstract}
We present Trinity, a ternary transformer inference engine on a \$30 Xilinx
Artix-7 FPGA (XC7A100T) using zero DSP48 blocks and a fully open-source
synthesis toolchain (Yosys, nextpnr-xilinx, Project X-Ray).  Weights are
constrained to $\{-1, 0, +1\}$, reducing multiply-accumulate to pure
add/subtract logic.

The core contribution is the Ternary MatMul Unit (TMU): a $K\!=\!32$ parallel
dot-product engine that reads 32 ternary weights per cycle from banked BRAMs
and reduces them through a 5-stage combinational adder tree.  This achieves
$26\times$ speedup over sequential accumulation while maintaining zero DSP
utilization.

A 3-block autoregressive pipeline---embedding lookup, three TrinityBlocks
(up-projection $243\!\to\!729$, ReLU, down-projection $729\!\to\!243$,
residual connection, shift-based RMSNorm), language-model head, and
argmax---generates tokens at 43,241 cycles/token, yielding
${\sim}1{,}879$~tok/s at 81.25~MHz.  The design consumes ${\sim}20$K~LUTs
(32\%), ${\sim}117.5$~BRAM36-equivalent tiles (87\%), and \textbf{0~DSP48E1}
blocks, storing 1,125,090 ternary weights on-chip.

Through four incremental optimizations---TMU parallelism ($K\!=\!1 \to 16
\to 32$) and clock frequency (50$\to$81.25~MHz)---throughput improves
$4.0\times$ from 469 to 1,879~tok/s at constant silicon cost.

Compared to prior FPGA ternary accelerators---TerEffic (U280, \$17K, 2,733
DSPs), TeLLMe~v2 (KV260, \$249, 1,200 DSPs), FlightLLM (U280, 2,733
DSPs)---Trinity achieves the lowest cost per tok/s (\$0.016) while requiring
no proprietary tools.  To our knowledge, this is the first zero-DSP ternary
transformer on a sub-\$50 FPGA with open-source synthesis.
\end{abstract}

\begin{IEEEkeywords}
Ternary neural network, FPGA, zero-DSP, open-source EDA, edge inference, transformer
\end{IEEEkeywords}

\end{document}
